Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-12 analysis/paper/paper.Rmd
Add reporting on parameters with detectable differences

## Analysis of Effects

@@

>>>>

@@

For brevity, only journals where the 95% CI fell outside the Region of Practical Equivalence (ROPE) are reported here.
For a full description of all parameters see (XXXXXX).
When predicting the availability of computational methods (code) availability, the effect of *Phytopathology* (Median = 2.55, 95% CI [0.73, 4.24]) had a 99.59% probability of being positive (> 0), 99.57% of being significant (> 0.05), and 99.12% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24803).
When predicting the availability of data availability, three journals were less likely to share data, with the others being unable to detect any effect.
The effect of *Crop Protection* (Median = -2.13, 95% CI [-4.15, -0.59]) had a 99.78% probability of being negative (< 0), 99.70% of being significant (< -0.05), and 99.16% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 19427).
The effect of *Plant Disease* (Median = -2.13, 95% CI [-4.14, -0.60]) had a 99.84% probability of being negative (< 0), 99.80% of being significant (< -0.05), and 99.15% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22687).
The effect of *Revista Mexicana Fitopatologia* (Median = -2.03, 95% CI [-4.09, -0.43]) had a 99.52% probability of being negative (< 0), 99.38% of being significant (< -0.05), and 98.38% of being large (< -0.30).
The estimation successfully converged (Rhat = 1.002) and the indices are reliable (ESS = 5769).

There was no effect detected for year when predicting the availability of computational methods (code) availability.
However, the effect of the publication year of 2016 on the availability of data (Median = 1.13, 95% CI [0.23, 2.05]) had a 99.27% probability of being positive (> 0), 99.08% of being significant (> 0.05), and 96.48% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 10707).
There was no detectable pattern in increasing or decreasing availability of data in the years examined.

There were no detectable effects when predicting the effects of the five-year impact factor on the availability of code or data.

The effect of the open access policy, open being TRUE, (Median = 0.08, 95% CI [-2.13, 2.26]) had a 52.95% probability of being positive (> 0), 51.12% of being significant (> 0.05), and 41.96% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 22528).

Following the Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework, we report the median of the posterior distribution and its 95% CI (Highest Density Interval), along the probability of direction (pd), the probability of significance and the probability of being large. The thresholds beyond which the effect is considered as significant (i.e., non-negligible) and large are |0.05| and |0.30|. Convergence and stability of the Bayesian sampling had been assessed using R-hat, which should be below 1.01 (Vehtari et al., 2019), and Effective Sample Size (ESS), which should be greater than 1000 (Burkner, 2017).
